GNSS-based displacement detection using Bayesian inference

### 2020-11-17 paper/manuscript.tex
add result sigma

\begin{figure}[htbp]
	\centering
	\includegraphics[width=10 cm]{v_bd9_3_up_mu}
	\caption{Histogram of posterior estimation of the mean in field experiment 1.}
	\label{fig_v_bd9_3_up_mu}
\end{figure} 
\begin{table*}[htbp]
	\centering
	%	\fontsize{6.5}{8}\selectfont
	\begin{threeparttable}
		\caption{Measured height before and after each movement of the object hanging on the plank in field experiment 1, unit (mm).}
		\label{tab_measured_height}
		\begin{tabular}{ccccccccc}
			\toprule
			&&&\textbf{1}&\textbf{2}&\textbf{3}&\textbf{4}&\textbf{5}&\textbf{mean}\cr
			\midrule
			\multirow{3}*{Step 1} 
			& & ${h_0}$    &371.0&370.9&370.9&371.1&370.9&370.96\\
			& & ${h_1}$    &341.0&341.1&341.5&341.9&341.0&341.30\\
			& & $\Delta h$ & -30.0& -29.8& -29.4& -29.2& -29.9&-29.66\\
			\hline
			\multirow{3}*{Step 2} 
			& & ${h_0}$    &340.5&340.1&340.0&340.0&340.1&340.14\\
			& & ${h_1}$    &313.0&312.9&312.9&313.0&313.0&312.96\\
			& & $\Delta h$ &-27.5& -27.2& -27.1& -27.0& -27.1& -27.18\\
			\bottomrule
		\end{tabular}
	\end{threeparttable}
\end{table*}
The $\mu_0$, $\mu_1$, and $\mu_2$ obtained by the mean of the posterior samples are -1446.03 mm, -1474.11 mm, and -1489.83 mm, respectively, and the two displacements obtained by the difference of these mean values are -28.08 mm, -15.72 mm, respectively. The two displacements measured by tape are -29.66 mm and -27.18 mm respectively. To our surprise, the displacement difference between the two methods at the two change points is 1.58 mm and 11.46 mm, respectively. The main reason is that the displacement control equipment is not completely controllable.

@@

\begin{table*}[h!t]
	\centering
	%	\fontsize{6.5}{8}\selectfont
	\begin{threeparttable}
		\caption{Measured height before and after each movement of the object hanging on the plank, unit (m).}
		\label{tab_measured_height}
		\begin{tabular}{ccccccccc}
			\toprule
			&&&\textbf{1}&\textbf{2}&\textbf{3}&\textbf{4}&\textbf{5}&\textbf{mean}\cr
			\midrule
			\multirow{3}*{Step 1} 
			& & ${h_0}$    &368.5&	368.9&	369.0&	368.9&	369.0&	368.9\\
			& & ${h_1}$    &348.1&	348.0&	348.0&	348.2&	348.3&	348.1\\
			& & $\Delta h$ & 20.4&	 20.9&	 21.0&	 20.7&	 20.7&	 20.7\\
			\hline               
			\multirow{3}*{Step 2}
			& & ${h_0}$    &347.5&	347.3&	347.6&	347.5&	347.4&	347.5\\
			& & ${h_1}$    &326.1&	326.3&	326.1&	326.0&	326.1&	326.1\\
			& & $\Delta h$ & 21.4&	 21.0&	 21.5&	 21.5&	 21.3&	 21.3\\
			\hline               
			\multirow{3}*{Step 3}
			& & ${h_0}$    &325.0&	325.1&	324.9&	325.0&	325.2&	325.0\\
			& & ${h_1}$    &305.5&	305.3&	305.4&	305.5&	305.6&	305.5\\
			& & $\Delta h$ & 19.5&	 19.8&	 19.5&	 19.5&	 19.6&	 19.6\\
			\bottomrule
		\end{tabular}
	\end{threeparttable}
\end{table*}
\begin{figure}[htbp]
	\centering
	\includegraphics[width=10 cm]{v_bd9_4_up_ts}
	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
	\label{fig_v_bd9_4_up_ts}
\end{figure}

>>>>

\begin{figure}[htbp]
	\centering
	\includegraphics[width=10 cm]{v_bd9_3_up_mu}
	\caption{Histogram of posterior estimation of the mean in field experiment 1.}
	\label{fig_v_bd9_3_up_mu}
\end{figure} 
\begin{table*}[htbp]
	\centering
	%	\fontsize{6.5}{8}\selectfont
	\begin{threeparttable}
		\caption{Measured height before and after each movement of the object hanging on the plank in field experiment 1, unit (mm).}
		\label{tab_measured_height}
		\begin{tabular}{ccccccccc}
			\toprule
			&&&\textbf{1}&\textbf{2}&\textbf{3}&\textbf{4}&\textbf{5}&\textbf{mean}\cr
			\midrule
			\multirow{3}*{Step 1} 
			& & ${h_0}$    &371.0&370.9&370.9&371.1&370.9&370.96\\
			& & ${h_1}$    &341.0&341.1&341.5&341.9&341.0&341.30\\
			& & $\Delta h$ & -30.0& -29.8& -29.4& -29.2& -29.9&-29.66\\
			\hline
			\multirow{3}*{Step 2} 
			& & ${h_0}$    &340.5&340.1&340.0&340.0&340.1&340.14\\
			& & ${h_1}$    &313.0&312.9&312.9&313.0&313.0&312.96\\
			& & $\Delta h$ &-27.5& -27.2& -27.1& -27.0& -27.1& -27.18\\
			\bottomrule
		\end{tabular}
	\end{threeparttable}
\end{table*}
The $\mu_0$, $\mu_1$, and $\mu_2$ obtained by the mean of the posterior samples are -1446.03 mm, -1474.11 mm, and -1489.83 mm, respectively, and the two displacements obtained by the difference of these mean values are -28.08 mm, -15.72 mm, respectively. The two displacements measured by tape are -29.66 mm and -27.18 mm respectively. To our surprise, the displacement difference between the two methods at the two change points is 1.58 mm and 11.46 mm, respectively. The main reason is that the displacement control device is not fully controllable. It can be seen from Fig. \ref{fig_v_bd9_3_up_ts} that before the second displacement change, the plank appears obvious floating when measuring with the tape. As shown in Fig. \ref{fig_v_bd9_3_up_sigma}, the estimated value of $\sigma$ is 12.58 mm through the posterior sample mean of $\sigma$.

@@

\begin{table*}[h!t]
	\centering
	%	\fontsize{6.5}{8}\selectfont
	\begin{threeparttable}
		\caption{Measured height before and after each movement of the object hanging on the plank, unit (mm).}
		\label{tab_measured_height}
		\begin{tabular}{ccccccccc}
			\toprule
			&&&\textbf{1}&\textbf{2}&\textbf{3}&\textbf{4}&\textbf{5}&\textbf{mean}\cr
			\midrule
			\multirow{3}*{Step 1} 
			& & ${h_0}$    &368.5&	368.9&	369.0&	368.9&	369.0&	368.9\\
			& & ${h_1}$    &348.1&	348.0&	348.0&	348.2&	348.3&	348.1\\
			& & $\Delta h$ & 20.4&	 20.9&	 21.0&	 20.7&	 20.7&	 20.7\\
			\hline               
			\multirow{3}*{Step 2}
			& & ${h_0}$    &347.5&	347.3&	347.6&	347.5&	347.4&	347.5\\
			& & ${h_1}$    &326.1&	326.3&	326.1&	326.0&	326.1&	326.1\\
			& & $\Delta h$ & 21.4&	 21.0&	 21.5&	 21.5&	 21.3&	 21.3\\
			\hline               
			\multirow{3}*{Step 3}
			& & ${h_0}$    &325.0&	325.1&	324.9&	325.0&	325.2&	325.0\\
			& & ${h_1}$    &305.5&	305.3&	305.4&	305.5&	305.6&	305.5\\
			& & $\Delta h$ & 19.5&	 19.8&	 19.5&	 19.5&	 19.6&	 19.6\\
			\bottomrule
		\end{tabular}
	\end{threeparttable}
\end{table*}
\begin{figure}[htbp]
	\centering
	\includegraphics[width=10 cm]{v_bd9_4_up_ts}
	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
	\label{fig_v_bd9_4_up_ts}
\end{figure}
